\bf A Concise Survey on Statistical Analysis in Bike Lane Research

### 2023-12-15 Manuscript/Manuscript.tex
edited conclusion section

In conclusion, this survey of statistical research on bike lanes offers a current snapshot of frequently used methods in the analysis of bike lanes. The significance of bike lanes in increasing cycling highlights the need for continued research and innovative statistical analysis to understand how to overcome the challenges of congestion, safety, and sustainability in transportation. This supports the efforts of enhancing cycling infrastructure for the benefits of individuals experiences while cycling and the betterment of entire communities.

>>>>

In conclusion, this survey of statistical research on bike lanes offers a current snapshot of frequently used methods in the analysis of bike lanes. When working in this field of study, the choice of the best statistical model should consider the specific research objectives, the characteristics of the available data, and the assumptions of the model. Often, a combination of different models or methodologies may be more informative to comprehensively understand various aspects of bike lane-related phenomena. Consulting with experts in specific techniques and conducting exploratory data analysis can also guide the selection of the most appropriate statistical approach for a given bike lane research study. \par

The significance of bike lanes in increasing cycling highlights the need for continued research and innovative statistical analysis to understand how to overcome the challenges of congestion, safety, and sustainability in transportation. As shown in this summary paper, such analysis is critical to support the efforts of enhancing cycling infrastructure for the benefits of individuals experiences while cycling and the betterment of entire communities.
